О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-18 pps-linear-bound/pps-linear-lower-bound.tex
estimation -> estimate

For every finite point set, its diameter is naturally defined as
\begin{equation}
	\operatorname{diam} M = \max_{A,B\in M} |AB|
	.
\end{equation}
The next emerging question is: how the diameter of an integral point set depends on its cardinality?
One can easily see that every $M\in\mathfrak{M}(m,n)$ with $\operatorname{diam} M = h$
can be dilated to $M_p\in\mathfrak{M}(m,n)$ with $\operatorname{diam} M = ph$
for every $p\in\mathbb{N}$.
So, the question above should be rephrased:
how \textit{the least possible} diameter of an integral point set depends on its cardinality?
To answer it, the following function was introduced~\cite{kurz2008bounds,kurz2008minimum}:
\begin{equation}
	d(m,n) = \min_{M\in\mathfrak{M}(m,n)} \operatorname{diam} M = \min_{M\in\mathfrak{M}(m,n)} \max_{A,B\in M} |AB|
	.
\end{equation}
We also refer to~\cite{kurz2008bounds} for a list of known exact values of $d(m,n)$
and estimations; in the present paper, the case of $m=2$ will mostly be in the focus.

@@

	\item
		estimate vs. bound vs. estimation

>>>>

For every finite point set, its diameter is naturally defined as
\begin{equation}
	\operatorname{diam} M = \max_{A,B\in M} |AB|
	.
\end{equation}
The next emerging question is: how the diameter of an integral point set depends on its cardinality?
One can easily see that every $M\in\mathfrak{M}(m,n)$ with $\operatorname{diam} M = h$
can be dilated to $M_p\in\mathfrak{M}(m,n)$ with $\operatorname{diam} M = ph$
for every $p\in\mathbb{N}$.
So, the question above should be rephrased:
how \textit{the least possible} diameter of an integral point set depends on its cardinality?
To answer it, the following function was introduced~\cite{kurz2008bounds,kurz2008minimum}:
\begin{equation}
	d(m,n) = \min_{M\in\mathfrak{M}(m,n)} \operatorname{diam} M = \min_{M\in\mathfrak{M}(m,n)} \max_{A,B\in M} |AB|
	.
\end{equation}
We also refer to~\cite{kurz2008bounds} for a list of known exact values of $d(m,n)$
and estimates; in the present paper, the case of $m=2$ will mostly be in the focus.

@@

	\item
		estimate vs. bound
